---
title: "RMarkdown Prueba 2"
author: "Beatriz Salas"
date: "19-08-2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(dplyr)
library(rmarkdown)
library(knitr)
library(kableExtra)
```

## Extint Plants Analysis 

This data base contain plant species that are extinct, including actions taken to avoid their extinction and the types of threats that caused their extinction.  

You can find the data base [here](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-08-18)

Let's call the data base running the next code:

```{r, message = FALSE, warning = FALSE}
plants <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-18/plants.csv')

actions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-18/actions.csv')

threats <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-08-18/threats.csv')
```

### Analysis of data base

We can extract some interesting information from this data base:

The number of extinct species by continent are showed in the next table:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
Table1 <- plants %>% 
 dplyr::group_by(continent) %>% 
 dplyr::count(continent) %>% 
 dplyr::rename(num_species = n)
  
kable(Table1) %>% 
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```
### Interesting facts

Before the year 1900 there were `r actions %>%  
  dplyr::filter(year_last_seen == "Before 1900") %>% nrow()`  extinct plants species already, and only in the past 20 years it has extincted other  `r actions %>% dplyr::filter(year_last_seen == "2000-2020") %>% nrow()` species. So there was a big amount of lost plant species during the human modern history. 
  
```{r, echo = FALSE, message = FALSE, warning = FALSE}
threats_notUK <- threats %>% 
  dplyr::filter(threat_type != "Unknown")
```

The are different threats that can cause the plant extinction, some of them are: `r unique(c(as.character(threats_notUK$threat_type))) `.

The next table show the amount of plant species that were exposed to each threat type:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
Table2 <- threats_notUK %>% 
    dplyr::group_by(threat_type) %>% 
    dplyr::count(threatened) %>%
    dplyr::filter(threatened == 1) %>% 
    dplyr::summarise(threat_type, n) %>% 
    dplyr::rename(Species_Number = n)
   
  
  kable(Table2) %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```




